\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{a4paper, margin=0.75in}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
}
\setlength{\parindent}{0pt}

% Custom section formatting
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Divy Pathak}} \\
    \vspace{5pt}
    \begin{tabular}{c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c}
        \href{https://termfolio-three.vercel.app}{Portfolio} & 
        \href{https://blog-excl.netlify.app/}{Blog} & 
        \href{https://github.com/divy-03}{GitHub}  
    \end{tabular} \\
    \vspace{5pt}
    \begin{tabular}{c@{\hskip 10pt}c@{\hskip 10pt}c@{\hskip 10pt}c}
        \href{https://www.linkedin.com/in/pathakdivy03}{LinkedIn} & 
        \href{mailto:pathakdivy03@gmail.com}{pathakdivy03@gmail.com} 
     \end{tabular} \\
\end{center}

% Education
\section*{Education}

\textbf{Vellore Institute of Technology, Bhopal} \hfill \textit{Sep 2022 – Present} \\
\textit{B.Tech in Computer Science and Engineering} \hfill \textbf{CGPA:} 7.72\\
Class XII \textbf{76.4}\% 
Class X \textbf{91.4}\%

% Projects
\section*{Projects}


\textbf{KickBid} (\href{https://github.com/divy-03/KickBid-client-js}{GitHub}/\href{https://kickbid.onrender.com}{Live}): A Web platform to facilitate sports tournaments. \\
KichBid will allow students to register as players, be rated based on their skills, and participate in an auction in which captains bid to form their teams. The platform provides real-time updates, team statistics, and tournament schedules, enhancing the experience for both players and spectators. It also offers an admin dashboard for managing events and ratings. \\
\textit{Technologies: HTML, CSS, Sass, React, JavaScript, MongoDB, Express, Node, RTK-Query}

\textbf{Leaf} (\href{https://github.com/divy-03/Leafront}{GitHub}/\href{https://leafront.vercel.com}{Live}): Client-side application for the Leafman back-end system \\
Developed a modern Next-based front-end to serve as the client for the \href{https://github.com/nightmare-tech/leafman}{leafman} back-end, implementing robust state management and seamless API integration using RTK Query. The project features a leaf-inspired loader, responsive UI design, and smooth animations powered by Framer Motion, ensuring both usability and aesthetics.\\
\textit{Technologies: NextJs, TypeScript, RTK Query, Tailwind CSS, Framer Motion, CSS}

\textbf{Carido}(\href{https://github.com/divy-03/car-app}{GitHub}/\href{https://carido.vercel.com}{Live}): AI-Powered Car Marketplace Web App \\
A full-stack car listing platform built with Next.js 15, Tailwind CSS, Prisma, and PostgreSQL. Integrated the Gemini API to enable AI-driven car search and auto-generate car details during listings. Features include advanced filtering, detailed car pages, image generation \& uploads via ImageKit, and seamless seller-buyer interaction. Deployed on Vercel with Prisma-managed Postgres (Neon) database. \\
\textit{Technologies: NextJs, Prisma, PostgreSQL, Tailwind CSS, ImageKit, Docker, NeonDB, Zustand, TypeScript, NextAuth, Zod }

\textbf{Personal Blog Website}(\href{https://github.com/divy-03/blog-website}{GitHub}/\href{https://blog-excl.netlify.app}{Live}): Static Blog Powered by Hugo \\
A personal blogging platform built with Hugo and customized using the Reimu theme. Tweaked layouts, colors, and assets to create a clean and minimal look for publishing Markdown-based posts. The site supports easy content management through Markdown files, auto-generates static pages, and is optimized for fast loading. Deployed seamlessly on Netlify with continuous deployment from GitHub. \\
\textit{Technologies: Hugo, Markdown, Netlify, Git, Static Site Generation }

% Technical Skills
\section*{Technical Skills}
\begin{itemize}[leftmargin=0.15in]
    \item \textbf{Frontend Development:} Next.js, React, Redux Toolkit, TypeScript, JavaScript, Tailwind CSS, Sass, HTML, CSS, Framer Motion, Plasmo
    \item \textbf{Backend Development:} Node.js, Express.js, Prisma, MongoDB, PostgreSQL, NeonDB, JSON-RPC, REST APIs, WebSockets
    \item \textbf{DevOps \& Tools:} Docker, CI/CD, Linux, Git/GitHub, Render, Vercel, Netlify
    \item \textbf{Programming Languages:} C++, Python, JavaScript, TypeScript, C
    \item \textbf{Other:} API Design, System Design Basics, Japanese Language (JLPT N5)
\end{itemize}

% Relevant Courses 
\section*{Relevant Courses \& Achievements}
\href{https://www.holopin.io/hacktoberfest2025/userbadge/cmheyey4z005pl704evj2qn0n}{Hacktoberfest Super Contributor 2025} \\
Contributed in Social Summer of Code SSOC 2025\\s
\href{https://courses.ibmcep.cognitiveclass.ai/certificates/a467c39f34664cf1872eb8525bf89cd1}{IBM - DevOps Fundamentals}\\
\href{https://courses.ibmcep.cognitiveclass.ai/certificates/39d2fc2434714ea7827efc7e9ede718b}{IBM - Agile Methodologies}\\
\href{https://courses.ibmcep.cognitiveclass.ai/certificates/a0eb39a3ce694851b2c2e1ce7ba05a42}{IBM - Devops, Agile \& Design Thinking}\\
\href{https://drive.google.com/file/d/1N50XuDdBnegwt5orYsi533G66o7I_ubz/view?usp=sharing}{JLPT - N5 Japanese}

% Interests
\section*{Interests}
Football | Piano | Fitness | Music

\end{document}x
